---
title: "What this package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What this package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(functionspackage)
```

# Introduction

This is a package of basic functions for MATH 4753.

# myread()

The myread() function is utilized for opening a CSV file of your choosing. You need only call "myread()" for this function to work.

# mybin()

The mybin() function creates a plot for a binomial simulation given certain parameters. You must call the function as follows:

mybin(iter = 100, n = 10, p = 0.7)

where *iter* is the number of iterations, *n* is the sample size, and *p* is the probability.

# myncurve()

The myncurve() function is used to find the area under a normal curve. You must call the function as follows:

myncurve(mu = 3, sigma = 2, a = 4)

where *mu* is the mean, *sigma* is the standard deviation, and *a* is the upper tail value.

# fire

This is a data set of the fire safety of doors.

# mycltp()

The mycltp() function is used to create many useful plots for a Poisson distribution. You must call the function as follows:

mycltp(n = 2, iter = 10000, lambda = 4)

where *n* is the sample size, *iter* is the number of iterations, and *lambda* is *iter* divided by *n*.

# myboot2()

The myboot2() function is used to create a bootstrap and provides a histogram of sample evaluation using requested function. You must call the function as follows:

myboot2(iter=10000,sam,fun="mean",alpha=0.30,cx=1.5

where *iter* is the number of iterations, *x* is the sample, *fun* is the function to evaluate with, and *alpha* is the bootstrap interval value (95% = 0.05).

# mymaxlik()

The mymaxlik() function is used to find the max likelihood value of a given sample and parameters, and provides index values for different variables and a graph illustrating the maximum likelihood value. You must call the function as follows:

mymaxlik(x = c(3, 3, 4, 3, 4, 5, 5, 4), param = seq(0, 1, length = 1000)

where *lfun* is the function to use (binomial, poisson, etc), *x* is a vector of values, *param* is the parameter to calculate (prob, theta, lambda, etc), and *...* are additional arguments, if needed.


